Supplemental Materials: \\ \emph{Active-contours driven registration method for structure-informed segmentation of diffusion MR images}

### 2015-04-08 Publications/2015-NeuroImage/06-discussion.tex
add some missing dois

\paragraph*{Application on real data}
We designed \emph{regseg} as a method to segment \gls*{dmri} data exploiting the
  anatomical information extracted in the corresponding \gls*{t1} image of the subject.
Applications of whole-brain tractography \citep{smith_tractbased_2006,craddock_imaging_2013}
  usually solve the problem in a two-step approach.
First, images are corrected for nonlinear distortions using auxiliary acquisitions
  such as fieldmaps \citep{jezzard_correction_1995}, \gls*{t2} images \citep{kybic_fast_2003},
  etc.
Second, the segmentation is projected from a reference \gls*{t1} image using linear
  registration \citep{greve_accurate_2009}.
\emph{Regseg} solves this joint problem in one single step, and it does not require any additional
  acquisition over the minimal protocol including \gls*{t1} and \gls*{dmri} images only.
This situation is commonly found in historical datasets.
Beyond the proposed application in \gls*{dmri} data, other potential uses of \emph{regseg} are
  atlas-based segmentation and tracking objects in time-series.

>>>>

\paragraph*{Application on real data}
We designed \emph{regseg} as a method to segment \gls*{dmri} data exploiting the
  anatomical information extracted in the corresponding \gls*{t1} image of the subject.
Applications of whole-brain tractography \citep{smith_tractbased_2006,craddock_imaging_2013}
  usually solve the problem in a two-step approach.
First, images are corrected for nonlinear distortions using auxiliary acquisitions
  such as fieldmaps \citep{jezzard_correction_1995}, \gls*{t2} images \citep{kybic_unwarping_2000},
  etc.
Second, the segmentation is projected from a reference \gls*{t1} image using linear
  registration \citep{greve_accurate_2009}.
\emph{Regseg} solves this joint problem in one single step, and it does not require any additional
  acquisition over the minimal protocol including \gls*{t1} and \gls*{dmri} images only.
This situation is commonly found in historical datasets.
Beyond the proposed application in \gls*{dmri} data, other potential uses of \emph{regseg} are
  atlas-based segmentation and tracking objects in time-series.
